### 2023-02-06 saturation-ver3/kt-formula-report1/kt-formula-report1.tex
interpolation
gluon may be negative??
grid plot|
notes

The other formulae( %Eqs.~(3.6)~and~(3.7) of Kimber's thesis with addition of scale $\mu$ as in 
Eqs.~(3.11)~and~(3.12) of Kimber's thesis ) are,
\begin{align}
\begin{split}
F_{2T}(x,Q^2)=\sum e^2_f\frac{Q^2}{4\pi}\int\frac{d k_t^2}{k_t^2}&\int^1_0 d\beta\int d \kappa_t ^2 \frac{d\phi}{2\pi}\alpha_s(\mu^2)\mathcal{F}(x/z,k^2_t,\mu^2)\Theta(1-x/z)\\
&\left[
\left[\beta^2+(1-\beta)^2\right]
\left(\frac{\boldsymbol{\kappa}_t}{D_1}-\frac{\boldsymbol{\kappa}_t-\mathbf{k}_t}{D_2}\right)^2
+m_f^2\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
\right]\label{eq:angle-unintegratedT}
\end{split}\\
\begin{split}
F_{2L}(x,Q^2)=\sum e^2_f\frac{Q^2}{4\pi}\int\frac{d k_t^2}{k_t^2}&\int^1_0 d\beta\int d \kappa_t ^2 \frac{d\phi}{2\pi}\alpha_s(\mu^2)\mathcal{F}(x/z,k^2_t,\mu^2)\Theta(1-x/z)\\
&\left[
4Q^2\beta^2 (1-\beta)^2\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
\right],\label{eq:angle-unintegratedL}
\end{split}
\end{align}
where
\begin{equation}
\begin{split}
D_1&=\kappa_t^2+\beta(1-\beta)Q^2+m_f^2\\
D_2&=(\boldsymbol{\kappa}_t-\mathbf{k}_t)^2+\beta(1-\beta)Q^2+m_f^2.
\end{split}
\end{equation}
%In this case, one has additional integral of $\phi$
Except for the coupling, this is $\phi$,  the angular part of $\kappa_t$, unintegrated version of Eq.~(\ref{eq:angle-integrated}) .
The scale for $\alpha_s$ is suggested to be 
\begin{equation}
\mu^2=k^2_t+\kappa^2+m_f^2.
\label{eq:scale}
\end{equation}
Note, the integration limits of $k_t$ and $\kappa_t$ are removed as GBW gluon is not perturbative.

@@

\input{r-formula}
\end{document}

>>>>

The other formulae( %Eqs.~(3.6)~and~(3.7) of Kimber's thesis with addition of scale $\mu$ as in 
Eqs.~(3.11)~and~(3.12) of Kimber's thesis ) are,
\begin{align}
\begin{split}
F_{2T}(x,Q^2)=\sum e^2_f\frac{Q^2}{4\pi}\int\frac{d k_t^2}{k_t^2}&\int^1_0 d\beta\int d \kappa_t ^2 \frac{d\phi}{2\pi}\alpha_s(\mu^2)\mathcal{F}(x/z,k^2_t,\mu^2)\Theta(1-x/z)\\
&\left[
\left[\beta^2+(1-\beta)^2\right]
\left(\frac{\boldsymbol{\kappa}_t}{D_1}-\frac{\boldsymbol{\kappa}_t-\mathbf{k}_t}{D_2}\right)^2
+m_f^2\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
\right]\label{eq:angle-unintegratedT}
\end{split}\\
\begin{split}
F_{2L}(x,Q^2)=\sum e^2_f\frac{Q^2}{4\pi}\int\frac{d k_t^2}{k_t^2}&\int^1_0 d\beta\int d \kappa_t ^2 \frac{d\phi}{2\pi}\alpha_s(\mu^2)\mathcal{F}(x/z,k^2_t,\mu^2)\Theta(1-x/z)\\
&\left[
4Q^2\beta^2 (1-\beta)^2\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
\right],\label{eq:angle-unintegratedL}
\end{split}
\end{align}
where
\begin{equation}
\begin{split}
D_1&=\kappa_t^2+\beta(1-\beta)Q^2+m_f^2\\
D_2&=(\boldsymbol{\kappa}_t-\mathbf{k}_t)^2+\beta(1-\beta)Q^2+m_f^2.
\end{split}
\end{equation}
%In this case, one has additional integral of $\phi$
Except for the coupling, this is $\phi$,  the angular part of $\kappa_t$, unintegrated version of Eq.~(\ref{eq:angle-integrated}) .
The scale for $\alpha_s$ is suggested to be 
\begin{equation}
\mu^2=k^2_t+\kappa^2+m_f^2.
\label{eq:scale}
\end{equation}
Note, the integration limits of $k_t$ and $\kappa_t$ are removed as GBW gluon is not perturbative.
\section{BGK}
In order to use the GBK dipole, one needs to evaluate
\begin{equation}
\begin{split}
	\alpha \mathcal{F}(x,k_t)&=\frac{3}{4\pi}\int \frac{d^2r}{(2\pi)^2}e^{-i\mathbf{r}\cdot\mathbf{k_t}}\nabla^2_r\sigma(x,r)\\
&=\frac{3}{8\pi^2}\int dr r J_0(r k_t) \nabla^2_r\sigma(x,r).
\end{split}
\end{equation}
While $\nabla^2_r\sigma(x,r)$ is relatively smooth function, $J_0(z)$ is oscillatory function imposing difficulty in integration. Thus one may approximate  $\nabla^2_r\sigma(x,r)$.

\subsection{Alternatively...}
$\nabla^2_r\sigma(x,r)$
 of GBW is 
\begin{equation}
\sigma_0 Q_s^2 \left(1-\frac{Q_s^2}{4}r^2\right)e^{-\frac{Q_s^2}{4}r^2}.
\end{equation}
and since
\begin{equation}
	\frac{3}{4\pi} \nabla^2_r\sigma(x,r)=\int d^2ke^{-i\mathbf{r}\cdot\mathbf{k_t}}\alpha \mathcal{F}(x,k_t),
\end{equation}
small-$r$ limit is
\begin{equation}
\begin{split}
	\lim_{r\rightarrow0}\frac{3}{4\pi} \nabla^2_r\sigma(x,r)&=\pi \int^{1/r}_0 dk^2\alpha \mathcal{F}(x,k_t)\\
&=\pi \alpha xg(x,1/r).
\end{split}
\end{equation}
For this, we can propose
\begin{equation}
Q_s^2=\frac{4\pi^2 \alpha x g(x,1/r)}{3\sigma_0},
\end{equation}
which is almost BGK.

\subsection{On running coupling of BGK}
\begin{equation}
\sigma(x,r)=\frac{4\pi}{N_c}\int\frac{d^2\mathbf{k}_t}{k_t^2}\left(1-e^{-i\mathbf{k}_t\cdot \mathbf{r}}\right)\alpha\mathcal{F}(x,k_t)
\end{equation}
in small-$r$ limit (for $k_t r\ll1$ considering large-$k_t$ region is irrelevant.), 
\begin{equation}
\begin{split}
\sigma(x,r)&=\frac{4\pi}{N_c}\int^{1/r^2}_0 dk^2_t\left(\frac{k_t^2r^2 \pi}{4}\right)\alpha\mathcal{F}(x,k_t^2)\\
&=\frac{\pi^2}{N_c}\int^{1/r^2}_0 dk^2_t \alpha\mathcal{F}(x,k_t^2)
\end{split}
\end{equation}
then in BGK,
\begin{equation}
%\begin{split}
=\frac{\pi^2}{N_c}\alpha xg(x,1/r^2).
%\end{split}
\end{equation}
But what exactly happened to $\alpha$? 
Usually the relation is 
\begin{equation}
xg(x,Q^2)=\int^{Q^2}_0 d k^2_t \mathcal{F}(x,k_t^2)
\end{equation}
without $\alpha$. 
if $\alpha=\alpha(\mu^2)$, the BGK derivation fails...
Also, note, that the argument of $\
alpha$ being $1/r$ may be a bit odd as it is not just $k^2_t$ in the $k_t$ formula.

@@

\input{r-formula}

\section{Log rise...}
\begin{equation}
\alpha \mathcal{F} =\frac{3}{8\pi^2}\int^\infty_0dr r J_0(r k)\nabla^2_r \sigma
\end{equation}
in small $k$ limit,
\begin{equation}
\begin{split}
\lim_{k\rightarrow0 } \alpha \mathcal{F} &=\frac{3}{8\pi^2}\int^\infty_0dr r \nabla^2_r \sigma\\
&=\frac{3}{8\pi^2}\int^\infty_0dr r\left[\frac{\partial^2\sigma}{\partial r^2}+\frac{\partial\sigma}{\partial r}\right]\\
&=\frac{3}{8\pi^2}\left[r\frac{\partial\sigma}{\partial r}-\int dr \frac{\partial\sigma}{\partial r} +\sigma \right]^\infty_0\\
&=\frac{3}{8\pi^2}\left[r\frac{\partial\sigma}{\partial r}\right]^\infty_0=\frac{3}{8\pi^2}\left[\frac{\partial\sigma}{\partial \log(r)}\right]^\infty_0
\end{split}
\end{equation}

\begin{figure}
\includegraphics[width=\textwidth]{./dipole1.png}
\caption{Dipole cross sections. Left: GBW, Right: BGK.}
\end{figure}
\begin{figure}
\includegraphics[width=\textwidth]{./gluon1.png}
\caption{Observe the new structure arizing from the DGLAP (larger-$k_t$ peak). When $x$ is small it becomes the dominant contributon. Also there is a narrow ridge around $x\sim1$. It is probably a saturation line, i.e. the line is not straight like in GBW case. {\color{green}Some change of variables may be helpfull...}   }
\end{figure}

\end{document}
